Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-07 ms.tex
more precise value for speed of light
starting more thorough motivation/background for FDS99 emission model

% mention that the two different emissivity power laws allow 
% the model to simultaneously explain narrow SED peak, and flattening
% of SED toward the millimeter
We adopt the thermal dust emission model of FDS99, which consists of two 
populations of dust grains emitting as MBBs, each with distinct 
emission/absorption characteristics. Importantly, the emissivity power law 
indices $\beta$ of the two species differ. The shape of this spectrum is given 
by:

@@

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 2997.92\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. The color correction factors
of Equation \ref{equ:bpcorr} are applied in the sense that 
$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
direct comparison to the \PLANCK~data products.

@@

This equation is quite similar to Equation \ref{equ:iras}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the flux density per solid
angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
Second, each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. We have adopted the 
strategy of predicting each band in its native units, whether MJy/sr or 
$K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for all 
$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
represents the conversion factor from $K_{CMB}$ to MJy/sr, given by 
\cite{planckresponse} Equation 32.

@@

@@

>>>>

% mention that the two different emissivity power laws allow 
% the model to simultaneously explain narrow SED peak, and flattening
% of SED toward the millimeter
At sufficiently high frequencies, Galactic thermal dust emission can be 
adequately modeled as a single MBB with power-law emissivity 
\citep[e.g. SFD;][]{planckdust}. However, it has long been recognized, 
particularly in view of the FIRAS spectra, that the dust SED flattens toward 
the millimeter in a manner which is not consistent with a simple extrapolation 
of the single-MBB model to low frequencies. In the diffuse ISM, \cite{reach95} 
found an improved fit to the FIRAS data using a superposition of two $\beta$=2 
MBBs, one representing a `hot' grain population ($T$$\approx$), the other a 
`cold' grain population ($T$$\approx$).

We adopt the thermal dust emission model of FDS99, which consists of two 
populations of dust grains emitting as MBBs, each with distinct 
emission/absorption characteristics. Importantly, the emissivity power law 
indices $\beta$ of the two species differ. The shape of this spectrum is given 
by:

@@

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 2997.92458\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. The color correction factors
of Equation \ref{equ:bpcorr} are applied in the sense that 
$b_{\nu_i}(T ,\beta)\times M_{\nu_{i,c}}$ is a prediction suitable for 
direct comparison to the \PLANCK~data products.

@@

This equation is quite similar to Equation \ref{equ:iras}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the flux density per solid
angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
Second, each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. We have adopted the 
strategy of predicting each band in its native units, whether MJy/sr or 
$K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for 
$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
represents the conversion factor from $K_{CMB}$ to MJy/sr, given by 
\cite{planckresponse} Equation 32.

@@

% make argument that, in models with f1 and the beta's constant, the choice
% of frequency at which tau is evaluated does not matter

@@

% cite Green appendix for details of deriving EBV_SSPP from Schlafly 11 data ?
